Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2016-03-03 draft.tex
small textual change in sec:structure

Both because of the presence of absorbing states and these state variables whose values persist from period to period, this is a dynamic game rather than a standard repeated game.

>>>>

Both because of the presence of absorbing states and these state variables whose values depend on their values in the previous period, this is a dynamic game rather than a standard repeated game.
